Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2018-10-25 paper/SI.tex
Makefile more flexible

\author{Hyung Gyu Park} \affiliation{Nanoscience for Energy Technology and Sustainability,
Department of Mechanical and Process Engineering,
Eidgenössische Technische Hochschule (ETH) Zürich,
Tannenstrasse 3, Zürich CH-8092, Switzerland.}
\affiliation{Mechanical Engineering, Pohang University of Science and
  Technology (POSTECH), 77 Cheongam-ro, Nam-gu, Pohang, Gyeongbuk,
  Republic of Korea.}
\email{iduserpark@gmail.com}

>>>>

\author{Hyung Gyu Park} \affiliation{Nanoscience for Energy Technology and Sustainability,
Department of Mechanical and Process Engineering,
Eidgenössische Technische Hochschule (ETH) Zürich,
Tannenstrasse 3, Zürich CH-8092, Switzerland.}
\alsoaffiliation{Mechanical Engineering, Pohang University of Science and
  Technology (POSTECH), 77 Cheongam-ro, Nam-gu, Pohang, Gyeongbuk,
  Republic of Korea.}
\email{iduserpark@gmail.com}
